---
title: "Samplig values from a log-normal distribution and visualizing it"
author: "Sarah Morillo Leonardo"
date: "22/09/2019"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE)
```
#### Description
This is part B. of the firts exercise of the lecture "Statistical Analysis of High Throughput Genomic and Transcriptomic Data". The exercise consists of sampling 100 values from a log-normal distribution (with mu=1 and sigma=0.25) and then visualize them with histograms using different scales.

##### Sampling values

Sample 100 values from a log-normal distribution with mu = 1 and sigma = 0.25.

```{r sample_values, include=TRUE}
n <- 100
vals <- rlnorm(n, meanlog = 1, sdlog = 0.25)
vals.df <- data.frame(LogNormalValues = vals)
```

##### Histograms

Histogram of the distribution

```{r hist, echo=FALSE, message=FALSE}
ggplot(data = vals.df, aes(LogNormalValues))+
  geom_histogram()
  #geom_histogram(binwidth = 0.15)
```


Now we want to get the histogram on the log scale, i.e. taking the log of the log-normal distributed values. But since we know that the log of a log-normally distributed random variable is normally distributed, we get normally distributed values and the following histogram:
 
```{r hist of logscaled , echo=FALSE, message=FALSE}
ggplot(data = log(vals.df), aes(LogNormalValues))+
  xlab("NormalValues")+
  geom_histogram()
```

The mean of the values drawn from the log-normal distribution is:  `r mean(vals)` and the variance: `r var(vals)`. 